---
title: "Présentation des différents résultats"
output: 
  html_document:
    css: other_file/TOC.css
date: "`r Sys.Date()`"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "outpout") })
---
```{r setup, include=FALSE, message = FALSE, warning = FALSE} 
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE #,
   # cache = TRUE
)
library(tidyverse)
library(gt)
source("S2_Source_mtg_new_card.R")
knitr::read_chunk("S2_Source_mtg_new_card.R")
```

Code available at [https://github.com/fbettega/Modern_data_analysis/tree/main/outpout/result](https://github.com/fbettega/Modern_data_analysis/tree/main/outpout/result)



**Please note that the data shown is a modified version of the data where all the pre-ban decks containing the Violent Outburst card have been ignored.**


# Methode
## Archetype definition
[Modify version of archetype definition](https://github.com/fbettega/Modern_FB_archetype) initial definition [from Badaro](https://github.com/Badaro/MTGOFormatData)

```{r}
proportion_format_fun <- function(nb,tot){
  percent = round(nb*100/tot,1)
  res <- paste0(nb,"/",tot,"(",percent,"%)")
  return(res)
}


df_export <- readRDS("data/data_meta_en_cours.rds")

Table_with_arch_count_and_sub_count <- df_export %>%
  select(
    # id,Week,Color,
    Archetype,Base_Archetype,ReferenceArchetype_Archetype) %>% 
  mutate(across(Archetype:ReferenceArchetype_Archetype, ~ as.numeric(table(.x)[as.character(.x)]), .names = "count_{.col}")) %>% 
  group_by(Archetype) %>% 
  mutate(across(Base_Archetype:ReferenceArchetype_Archetype, ~ as.numeric(table(.x)[as.character(.x)]), .names = "count_in_arch_{.col}")) %>% 
  distinct() %>% 
  arrange(desc(count_Archetype)) %>% 
  mutate(Archetype = paste0("**",Archetype,"**"," (n :",count_Archetype, ")"),
         proportion_Base_Arch_in_Arch = 
           proportion_format_fun(
             count_in_arch_Base_Archetype,
             count_Archetype
             ),
         proportion_Arch_in_Base_Arch = 
           proportion_format_fun(
             count_in_arch_Base_Archetype,
             count_Base_Archetype
             ),
          proportion_Ref_Arch_in_Arch = 
           proportion_format_fun(
             count_in_arch_ReferenceArchetype_Archetype,
             count_Archetype
             ),
         proportion_Arch_in_Ref_Arch = 
           proportion_format_fun(
             count_in_arch_ReferenceArchetype_Archetype,
             count_ReferenceArchetype_Archetype
             )
         ) %>% 
  select(Archetype,
         Base_Archetype,
         ReferenceArchetype_Archetype,
         starts_with("proportion_")
         ) %>% 
  rename(Custom = Base_Archetype,
         Reference = ReferenceArchetype_Archetype
         )

```





<!---
Reste a détailler le groupement probablement tableau
-->

<!---
CI computation
-->
<!---
Type of tournament 
<!---
Tournament with matchup
-->


# Outpout
## [New card](/result/1_new_card.html)

Contains an analysis of the cards limited to certain recent sets to assess the impact of the new cards on each archetypes.

## [Presence archetype](/result/2_presence_archetype.html)

<!---
potentiellement selecteur de deck sous contrainte en script annexe
-->

```{r, Introduction_chunk_2_Deck_analysis, results='asis'}

```

### [Top 8 deck](/result/7_last_weeks_winners.html)

```{r, Introduction_chunk_7_top8, results='asis'}

```

## Card win rate analysis  


### [Card win rate table](/result/3_Card_win_rate_table.html)
```{r, Introduction_chunk_3_Deck_analysis, results='asis'}

```

### [Cards WR models](/result/5_Deck_analysis.html)
```{r, Introduction_chunk_5_Deck_analysis, results='asis'}

```

## [Matrix WR](/result/4_matrix_WR.html)
```{r, Introduction_chunk_4_Deck_analysis, results='asis'}

```


## [Best deck analysis](/result/6_best_deck.html)

```{r, Introduction_chunk_6_best_deck, results='asis'}

```

# Archetype aggregation  

```{r results='asis'}
title_table <- paste0("**Tabler summarise how the archetypes are aggregated**")

Subtitle <- paste0(
  "[Custom](https://github.com/fbettega/Modern_FB_archetype) corresponds to my definition of archetypes, also shown as *Base_archetype* in the data \n
[Reference](https://github.com/Badaro/MTGOFormatData) corresponds to Badaro definition of archetypes, also shown as *Reference_archetype* in the data 
  "
)

Table_with_arch_count_and_sub_count  %>%

  gt::gt(groupname_col = "Archetype") %>%  
  gt::text_transform(
    locations = cells_row_groups(),
    fn = function(x) {
      lapply(x, function(x) {
        gt::md(x)
      })
     }
  ) %>% 
  tab_options(row_group.as_column = TRUE) %>% 
  tab_spanner(
    label = md("**Parser**"),
    columns = c(Custom, Reference)
  )  %>% 
  tab_spanner(
    label = md("**Custom**"),
    columns = c(proportion_Base_Arch_in_Arch,proportion_Arch_in_Base_Arch)
  ) %>% 
  tab_spanner(
    label = md("**Reference**"),
    columns = c(proportion_Ref_Arch_in_Arch,proportion_Arch_in_Ref_Arch)
  ) %>% 
   cols_label(
    proportion_Base_Arch_in_Arch = md("Percent Archetype"),
    proportion_Arch_in_Base_Arch = md("Percent Sub Archetype"),
    proportion_Ref_Arch_in_Arch = md("Percent Archetype"),
    proportion_Arch_in_Ref_Arch = md("Percent Sub Archetype")
  ) %>%
  gt::cols_align(
    align = c("center"),
    columns = everything()
  ) %>% 
  gt::tab_header(
    title = gt::md(title_table),
    subtitle = gt::md(Subtitle)
  ) %>% 
  gt::tab_options(
    # column_labels.hidden = TRUE,
    table.layout = "Auto"
    )
```


# Acknowledgements

Thanks to [Badaro](https://github.com/Badaro) for his data collection work and the archetype parser.
Thanks to [Aliquanto](https://github.com/Aliquanto3) for his initial analysis, which served as an inspiration for me.


