---
title: "Présentation des différents résultats"
output: 
  html_document:
date: "`r Sys.Date()`"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "outpout") })
---
```{r setup, include=FALSE, message = FALSE, warning = FALSE} 
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE #,
   # cache = TRUE
)
source("S2_Source_mtg_new_card.R")
knitr::read_chunk("S2_Source_mtg_new_card.R")
```

Code available at [https://github.com/fbettega/Modern_data_analysis/tree/main/outpout/result](https://github.com/fbettega/Modern_data_analysis/tree/main/outpout/result)



# Methode
## Archetype definition
[Modify version of archetype definition](https://github.com/fbettega/Modern_FB_archetype) initial definition [from Badaro](https://github.com/Badaro/MTGOFormatData)

<!---
Reste a détailler le groupement probablement tableau
-->

<!---
CI computation
-->
<!---
Type of tournament 
<!---
Tournament with matchup
-->


# Outpout
## [New card](/result/1_new_card.html)

Contains an analysis of the cards limited to certain recent sets to assess the impact of the new cards on each archetypes.

## [Presence archetype](/result/2_presence_archetype.html)

<!---
Add winner deck of last 2 weeks perhaps in another script
potentiellement selecteur de deck sous contrainte en script annexe
-->

```{r, Introduction_chunk_2_Deck_analysis, results='asis'}

```

### [Top 8 deck](/result/7_last_weeks_winners.html)

```{r, Introduction_chunk_7_Deck_analysis, results='asis'}

```

## Card win rate analysis  


### [Card win rate table](/result/3_Card_win_rate_table.html)
```{r, Introduction_chunk_3_Deck_analysis, results='asis'}

```

### [Cards WR models](/result/5_Deck_analysis.html)
```{r, Introduction_chunk_5_Deck_analysis, results='asis'}

```

## [Matrix WR](/result/4_matrix_WR.html)
```{r, Introduction_chunk_4_Deck_analysis, results='asis'}

```


## [Best deck analysis](/result/6_best_deck.html)
<!---
Inclure les variables en les extrayant des rmd concerné 
-->
```{r, Introduction_chunk_6_best_deck, results='asis'}

```




