## Amulet Titan

### Global deck models 

:::::::::::::: {.columns}

::: {.column width="50%"}


```{r results = 'asis'}

print(htmltools::tagList(res_global_gt_table[["Amulet Titan"]]$any))

```

:::
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_global_gt_table[["Amulet Titan"]]$count))
```
:::

::::::::::::::
### Separate model for main and side 

#### Mainboard 
:::::::::::::: {.columns}
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Amulet Titan"]]$any$main))
```

:::::: {.column width="50%"}

```{r results = 'asis'}
htmltools::tagList(res_main_and_side_gt_table[["Amulet Titan"]]$count$main)
```
:::
::::::::::::::
#### Sideboard 
:::::::::::::: {.columns}
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Amulet Titan"]]$any$side))
```

:::
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Amulet Titan"]]$count$side))
```
:::
::::::::::::::


## Burn

### Global deck models 

:::::::::::::: {.columns}

::: {.column width="50%"}


```{r results = 'asis'}

print(htmltools::tagList(res_global_gt_table[["Burn"]]$any))

```

:::
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_global_gt_table[["Burn"]]$count))
```
:::

::::::::::::::
### Separate model for main and side 

#### Mainboard 
:::::::::::::: {.columns}
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Burn"]]$any$main))
```

:::::: {.column width="50%"}

```{r results = 'asis'}
htmltools::tagList(res_main_and_side_gt_table[["Burn"]]$count$main)
```
:::
::::::::::::::
#### Sideboard 
:::::::::::::: {.columns}
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Burn"]]$any$side))
```

:::
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Burn"]]$count$side))
```
:::
::::::::::::::


## Coffers Control

### Global deck models 

:::::::::::::: {.columns}

::: {.column width="50%"}


```{r results = 'asis'}

print(htmltools::tagList(res_global_gt_table[["Coffers Control"]]$any))

```

:::
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_global_gt_table[["Coffers Control"]]$count))
```
:::

::::::::::::::
### Separate model for main and side 

#### Mainboard 
:::::::::::::: {.columns}
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Coffers Control"]]$any$main))
```

:::::: {.column width="50%"}

```{r results = 'asis'}
htmltools::tagList(res_main_and_side_gt_table[["Coffers Control"]]$count$main)
```
:::
::::::::::::::
#### Sideboard 
:::::::::::::: {.columns}
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Coffers Control"]]$any$side))
```

:::
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Coffers Control"]]$count$side))
```
:::
::::::::::::::


## Eldrazi

### Global deck models 

:::::::::::::: {.columns}

::: {.column width="50%"}


```{r results = 'asis'}

print(htmltools::tagList(res_global_gt_table[["Eldrazi"]]$any))

```

:::
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_global_gt_table[["Eldrazi"]]$count))
```
:::

::::::::::::::
### Separate model for main and side 

#### Mainboard 
:::::::::::::: {.columns}
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Eldrazi"]]$any$main))
```

:::::: {.column width="50%"}

```{r results = 'asis'}
htmltools::tagList(res_main_and_side_gt_table[["Eldrazi"]]$count$main)
```
:::
::::::::::::::
#### Sideboard 
:::::::::::::: {.columns}
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Eldrazi"]]$any$side))
```

:::
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Eldrazi"]]$count$side))
```
:::
::::::::::::::


## Living End

### Global deck models 

:::::::::::::: {.columns}

::: {.column width="50%"}


```{r results = 'asis'}

print(htmltools::tagList(res_global_gt_table[["Living End"]]$any))

```

:::
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_global_gt_table[["Living End"]]$count))
```
:::

::::::::::::::
### Separate model for main and side 

#### Mainboard 
:::::::::::::: {.columns}
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Living End"]]$any$main))
```

:::::: {.column width="50%"}

```{r results = 'asis'}
htmltools::tagList(res_main_and_side_gt_table[["Living End"]]$count$main)
```
:::
::::::::::::::
#### Sideboard 
:::::::::::::: {.columns}
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Living End"]]$any$side))
```

:::
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Living End"]]$count$side))
```
:::
::::::::::::::


## Merfolk

### Global deck models 

:::::::::::::: {.columns}

::: {.column width="50%"}


```{r results = 'asis'}

print(htmltools::tagList(res_global_gt_table[["Merfolk"]]$any))

```

:::
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_global_gt_table[["Merfolk"]]$count))
```
:::

::::::::::::::
### Separate model for main and side 

#### Mainboard 
:::::::::::::: {.columns}
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Merfolk"]]$any$main))
```

:::::: {.column width="50%"}

```{r results = 'asis'}
htmltools::tagList(res_main_and_side_gt_table[["Merfolk"]]$count$main)
```
:::
::::::::::::::
#### Sideboard 
:::::::::::::: {.columns}
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Merfolk"]]$any$side))
```

:::
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Merfolk"]]$count$side))
```
:::
::::::::::::::


## Murktide

### Global deck models 

:::::::::::::: {.columns}

::: {.column width="50%"}


```{r results = 'asis'}

print(htmltools::tagList(res_global_gt_table[["Murktide"]]$any))

```

:::
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_global_gt_table[["Murktide"]]$count))
```
:::

::::::::::::::
### Separate model for main and side 

#### Mainboard 
:::::::::::::: {.columns}
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Murktide"]]$any$main))
```

:::::: {.column width="50%"}

```{r results = 'asis'}
htmltools::tagList(res_main_and_side_gt_table[["Murktide"]]$count$main)
```
:::
::::::::::::::
#### Sideboard 
:::::::::::::: {.columns}
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Murktide"]]$any$side))
```

:::
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Murktide"]]$count$side))
```
:::
::::::::::::::


## Nadu

### Global deck models 

:::::::::::::: {.columns}

::: {.column width="50%"}


```{r results = 'asis'}

print(htmltools::tagList(res_global_gt_table[["Nadu"]]$any))

```

:::
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_global_gt_table[["Nadu"]]$count))
```
:::

::::::::::::::
### Separate model for main and side 

#### Mainboard 
:::::::::::::: {.columns}
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Nadu"]]$any$main))
```

:::::: {.column width="50%"}

```{r results = 'asis'}
htmltools::tagList(res_main_and_side_gt_table[["Nadu"]]$count$main)
```
:::
::::::::::::::
#### Sideboard 
:::::::::::::: {.columns}
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Nadu"]]$any$side))
```

:::
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Nadu"]]$count$side))
```
:::
::::::::::::::


## Prowess

### Global deck models 

:::::::::::::: {.columns}

::: {.column width="50%"}


```{r results = 'asis'}

print(htmltools::tagList(res_global_gt_table[["Prowess"]]$any))

```

:::
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_global_gt_table[["Prowess"]]$count))
```
:::

::::::::::::::
### Separate model for main and side 

#### Mainboard 
:::::::::::::: {.columns}
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Prowess"]]$any$main))
```

:::::: {.column width="50%"}

```{r results = 'asis'}
htmltools::tagList(res_main_and_side_gt_table[["Prowess"]]$count$main)
```
:::
::::::::::::::
#### Sideboard 
:::::::::::::: {.columns}
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Prowess"]]$any$side))
```

:::
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Prowess"]]$count$side))
```
:::
::::::::::::::


## Reanimator

### Global deck models 

:::::::::::::: {.columns}

::: {.column width="50%"}


```{r results = 'asis'}

print(htmltools::tagList(res_global_gt_table[["Reanimator"]]$any))

```

:::
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_global_gt_table[["Reanimator"]]$count))
```
:::

::::::::::::::
### Separate model for main and side 

#### Mainboard 
:::::::::::::: {.columns}
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Reanimator"]]$any$main))
```

:::::: {.column width="50%"}

```{r results = 'asis'}
htmltools::tagList(res_main_and_side_gt_table[["Reanimator"]]$count$main)
```
:::
::::::::::::::
#### Sideboard 
:::::::::::::: {.columns}
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Reanimator"]]$any$side))
```

:::
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Reanimator"]]$count$side))
```
:::
::::::::::::::


## RWx aggro

### Global deck models 

:::::::::::::: {.columns}

::: {.column width="50%"}


```{r results = 'asis'}

print(htmltools::tagList(res_global_gt_table[["RWx aggro"]]$any))

```

:::
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_global_gt_table[["RWx aggro"]]$count))
```
:::

::::::::::::::
### Separate model for main and side 

#### Mainboard 
:::::::::::::: {.columns}
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["RWx aggro"]]$any$main))
```

:::::: {.column width="50%"}

```{r results = 'asis'}
htmltools::tagList(res_main_and_side_gt_table[["RWx aggro"]]$count$main)
```
:::
::::::::::::::
#### Sideboard 
:::::::::::::: {.columns}
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["RWx aggro"]]$any$side))
```

:::
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["RWx aggro"]]$count$side))
```
:::
::::::::::::::


## Scam

### Global deck models 

:::::::::::::: {.columns}

::: {.column width="50%"}


```{r results = 'asis'}

print(htmltools::tagList(res_global_gt_table[["Scam"]]$any))

```

:::
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_global_gt_table[["Scam"]]$count))
```
:::

::::::::::::::
### Separate model for main and side 

#### Mainboard 
:::::::::::::: {.columns}
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Scam"]]$any$main))
```

:::::: {.column width="50%"}

```{r results = 'asis'}
htmltools::tagList(res_main_and_side_gt_table[["Scam"]]$count$main)
```
:::
::::::::::::::
#### Sideboard 
:::::::::::::: {.columns}
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Scam"]]$any$side))
```

:::
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Scam"]]$count$side))
```
:::
::::::::::::::


## Storm

### Global deck models 

:::::::::::::: {.columns}

::: {.column width="50%"}


```{r results = 'asis'}

print(htmltools::tagList(res_global_gt_table[["Storm"]]$any))

```

:::
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_global_gt_table[["Storm"]]$count))
```
:::

::::::::::::::
### Separate model for main and side 

#### Mainboard 
:::::::::::::: {.columns}
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Storm"]]$any$main))
```

:::::: {.column width="50%"}

```{r results = 'asis'}
htmltools::tagList(res_main_and_side_gt_table[["Storm"]]$count$main)
```
:::
::::::::::::::
#### Sideboard 
:::::::::::::: {.columns}
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Storm"]]$any$side))
```

:::
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Storm"]]$count$side))
```
:::
::::::::::::::


## Tron

### Global deck models 

:::::::::::::: {.columns}

::: {.column width="50%"}


```{r results = 'asis'}

print(htmltools::tagList(res_global_gt_table[["Tron"]]$any))

```

:::
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_global_gt_table[["Tron"]]$count))
```
:::

::::::::::::::
### Separate model for main and side 

#### Mainboard 
:::::::::::::: {.columns}
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Tron"]]$any$main))
```

:::::: {.column width="50%"}

```{r results = 'asis'}
htmltools::tagList(res_main_and_side_gt_table[["Tron"]]$count$main)
```
:::
::::::::::::::
#### Sideboard 
:::::::::::::: {.columns}
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Tron"]]$any$side))
```

:::
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Tron"]]$count$side))
```
:::
::::::::::::::


## UBlackX Control

### Global deck models 

:::::::::::::: {.columns}

::: {.column width="50%"}


```{r results = 'asis'}

print(htmltools::tagList(res_global_gt_table[["UBlackX Control"]]$any))

```

:::
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_global_gt_table[["UBlackX Control"]]$count))
```
:::

::::::::::::::
### Separate model for main and side 

#### Mainboard 
:::::::::::::: {.columns}
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["UBlackX Control"]]$any$main))
```

:::::: {.column width="50%"}

```{r results = 'asis'}
htmltools::tagList(res_main_and_side_gt_table[["UBlackX Control"]]$count$main)
```
:::
::::::::::::::
#### Sideboard 
:::::::::::::: {.columns}
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["UBlackX Control"]]$any$side))
```

:::
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["UBlackX Control"]]$count$side))
```
:::
::::::::::::::


## URedX Control

### Global deck models 

:::::::::::::: {.columns}

::: {.column width="50%"}


```{r results = 'asis'}

print(htmltools::tagList(res_global_gt_table[["URedX Control"]]$any))

```

:::
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_global_gt_table[["URedX Control"]]$count))
```
:::

::::::::::::::
### Separate model for main and side 

#### Mainboard 
:::::::::::::: {.columns}
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["URedX Control"]]$any$main))
```

:::::: {.column width="50%"}

```{r results = 'asis'}
htmltools::tagList(res_main_and_side_gt_table[["URedX Control"]]$count$main)
```
:::
::::::::::::::
#### Sideboard 
:::::::::::::: {.columns}
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["URedX Control"]]$any$side))
```

:::
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["URedX Control"]]$count$side))
```
:::
::::::::::::::


## UWhiteX Control

### Global deck models 

:::::::::::::: {.columns}

::: {.column width="50%"}


```{r results = 'asis'}

print(htmltools::tagList(res_global_gt_table[["UWhiteX Control"]]$any))

```

:::
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_global_gt_table[["UWhiteX Control"]]$count))
```
:::

::::::::::::::
### Separate model for main and side 

#### Mainboard 
:::::::::::::: {.columns}
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["UWhiteX Control"]]$any$main))
```

:::::: {.column width="50%"}

```{r results = 'asis'}
htmltools::tagList(res_main_and_side_gt_table[["UWhiteX Control"]]$count$main)
```
:::
::::::::::::::
#### Sideboard 
:::::::::::::: {.columns}
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["UWhiteX Control"]]$any$side))
```

:::
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["UWhiteX Control"]]$count$side))
```
:::
::::::::::::::


## Yawgmoth

### Global deck models 

:::::::::::::: {.columns}

::: {.column width="50%"}


```{r results = 'asis'}

print(htmltools::tagList(res_global_gt_table[["Yawgmoth"]]$any))

```

:::
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_global_gt_table[["Yawgmoth"]]$count))
```
:::

::::::::::::::
### Separate model for main and side 

#### Mainboard 
:::::::::::::: {.columns}
::: {.column width="50%"}
```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Yawgmoth"]]$any$main))
```

:::::: {.column width="50%"}

```{r results = 'asis'}
htmltools::tagList(res_main_and_side_gt_table[["Yawgmoth"]]$count$main)
```
:::
::::::::::::::
#### Sideboard 
:::::::::::::: {.columns}
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Yawgmoth"]]$any$side))
```

:::
::: {.column width="50%"}

```{r results = 'asis'}
print(htmltools::tagList(res_main_and_side_gt_table[["Yawgmoth"]]$count$side))
```
:::
::::::::::::::


