---
title: "Archetype definition and other debug results"
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE} 
library(binom)
library("rjson")
library(kableExtra)
library(tidyverse)
library(scryr)
source("../sources/S2_Source_mtg_new_card.R",local = TRUE)

conflicted::conflicts_prefer(dplyr::filter)
params <- read_rds( "../data/intermediate_result/temp_format_encours_for_param.rds")
```


```{r data_reading }
df_export <-  readRDS(paste0("../data/",params$format_param,"_data_meta_en_cours.rds")) %>%
      # include filter bad deck
  filter(Valide_deck) %>% 
  mutate(
    Deck_winrate = Wins / (Losses + Wins)
  ) %>%
  group_by(Archetype) %>% 
  mutate(
    Archetype_count = n()
  ) %>% 
    ungroup() 

```





```{r cards_in_archetype_definition_computation}
merge_df_side_main <- 
  rbind(
  df_export %>%
  unnest_longer(Mainboard) %>%
  unnest_wider(Mainboard, names_sep = "_")  %>%
  select(Mainboard_Count,Mainboard_CardName,Archetype,Base_Archetype,id) %>%
  rename(Count = 1 , CardName = 2)   %>%
  mutate(main_side = "Main"),
  df_export %>%
  unnest_longer(Sideboard) %>%
  unnest_wider(Sideboard, names_sep = "_") %>%
  select(Sideboard_Count,Sideboard_CardName,Archetype,Base_Archetype,id) %>%
  rename(Count = 1 , CardName = 2) %>%
  mutate(main_side = "Side")
  ) 

Deck_list_cards_count <- 
  rbind(
    merge_df_side_main,
  merge_df_side_main %>% 
    mutate(main_side = "Any") %>% 
  group_by(
    id,
    main_side,
    CardName,
    Archetype,
    Base_Archetype
    ) %>% 
  summarise(Count = sum(Count),.groups = "drop") 
  ) %>% 
  group_by( 
    Archetype,
    Base_Archetype
    ) %>% 
  mutate(Archetype_count = n_distinct(id)) %>% 
  group_by(
    main_side,
    CardName,
    Count,
    Archetype,
    Base_Archetype,
    Archetype_count
    ) %>% 
  summarise(N = n(),.groups = "drop") 


Deck_list_cards_count_with_any <- rbind(
  Deck_list_cards_count,
  Deck_list_cards_count %>% 
    mutate(Count = "Any") %>% 
  group_by(
    main_side,
    CardName,
    Count,
    Archetype,
    Base_Archetype,
    Archetype_count
    ) %>% 
  summarise(N = sum(N),.groups = "drop") 
  ) %>% 
  mutate(
    percent_presence = N/Archetype_count
  ) %>% 
  arrange(desc(Archetype_count)) %>% 
  mutate(across(where(is.character),as.factor))
# rm(Deck_list_cards_count)
```



# Cards in Archetype based arch combination  


```{r cards_in_archetype_definition_print}
htmltools::tagList(
      DT::datatable( 
        Deck_list_cards_count_with_any,
        colnames = str_replace_all(colnames(Deck_list_cards_count_with_any), "_", " "),
             callback = DT::JS(
      return_filter_js()
    ),     
  filter = "top",
  rownames = FALSE,
  options = list(
  dom = "ltipr",
    searchCols = list(
    list(search = '["Any"]' ),
    NULL,
    list(search = '["Any"]' ),
    NULL,NULL,NULL,NULL,NULL
  ),
  autoWidth = TRUE,
  pageLength = 25)
  )  %>% 
  DT::formatPercentage(c("percent_presence"),digits = 1)
  )
```


# Proximity

negative numbers are explicable because Y to X is positive.

```{r proximity_classif_loading}
proximty_classif <- read.csv(
  paste0("../data/intermediate_result/",
         params$format_param,"_proxymity_archetype_group.csv")) %>% 
          mutate(
            Archetype_proximity = as.factor(Archetype_proximity),
            value = as.factor(value)
                 ) %>% 
          rename(
            `Total archetype name` = Archetype_proximity ,
            `Base archetype name group` = value 
            ) %>% 
  as_tibble()

```


```{r proximity_classif_print}
htmltools::tagList(
      DT::datatable( 
        proximty_classif ,
             callback = DT::JS(
      return_filter_js()
    ),     
  filter = "top",
  rownames = FALSE,
  options = list(
  dom = "ltipr",
  autoWidth = TRUE,
  pageLength = 25)  ,
  escape=FALSE
  ) %>% 
    DT::formatRound(c(3:5), digits = 2)
  )

```



# Scryfall join not matching cards   

Just list all distinct cards in format with boolean if match or not with my scryfall join function.

```{r scryfall_db_matching_datareading}
modern_DB_card <- read_csv("../data/mtg_data/DBcarte_oracle.csv",show_col_types = FALSE) %>% 
   filter(
     !!sym(paste0("legalities.",tolower(params$format_param))) == "legal"
     )


test_scry_fall_on_all_cards <- 
  rbind(
    df_export %>%
    unnest_longer(Mainboard) %>%
    unnest_wider(Mainboard, names_sep = "_") %>% 
  select(Mainboard_CardName) %>%
  rename(CardName = Mainboard_CardName) ,
    df_export %>%
    unnest_longer(Sideboard) %>%
    unnest_wider(Sideboard, names_sep = "_") %>% 
  select(Sideboard_CardName) %>%
  rename(CardName = Sideboard_CardName) 
  )

```




```{r scryfall_db_matching_computation}
scry_fall_join_test_res <- join_with_scryfall(
    Df_with_cardname = test_scry_fall_on_all_cards,
    cardname_col = "CardName",
    scry_fall_df = modern_DB_card
                                 )
```


only show non matching cards no bug if table is empty.
Number of cards correctly match : `r sum(!is.na(scry_fall_join_test_res$scry_fall_id))` (`r round(sum(!is.na(scry_fall_join_test_res$scry_fall_id))*100/nrow(scry_fall_join_test_res),2)` %)



```{r scryfall_db_matching_print}
htmltools::tagList(
      DT::datatable( 
        scry_fall_join_test_res %>% 
          mutate(
            `parsing fail` = is.na(scry_fall_id),
            CardName = as.factor(CardName)
          ) %>% 
          select(-scry_fall_id) %>% 
          arrange(desc(`parsing fail`)
                  ),
      # colnames = str_replace_all(colnames(model_pred), "_", " "),
             callback = DT::JS(
      return_filter_js()
    ),     
  filter = "top",
  rownames = FALSE,
  options = list(
  dom = "ltipr",
  searchCols = list(
    NULL,
    list(search = '["true"]' )
  ),
  autoWidth = TRUE,
  pageLength = 25)  ,
  escape=FALSE
  ) 
  )


```







# Prediction and deck list

```{r model_prediction_reading}
# note pour FB du futur l'ordre compte et si cette table est affiché en premier les 
# autres ne fonctionne pas

Base_prediction_df <- read_rds(
  paste0("../data/intermediate_result/",params$format_param,"_result_pred.rds")
  )

model_pred <- left_join(
  inner_join(
    Base_prediction_df$table_each_model_pred %>%
      rename(Archetype = Archetype.x) %>%
      select(-Archetype.y) %>% select(-AnchorUri),
    vote_pred <- Base_prediction_df$table_vote_pred %>%
      select(-Archetype) %>%
      rename(
        Voting_Arch = name,
        Voting_result = value
      ),
    by = join_by(id)
  ),
  df_export %>%
    select(id, ReferenceArchetype_Archetype, parser_base_arch, Base_Archetype, Color),
  by = join_by(id)
) %>% 
  select(-id) %>% 
  relocate(
    ReferenceArchetype_Archetype, parser_base_arch,
    Base_Archetype, Color,Voting_Arch,Voting_result,
    .after = Archetype
           )  %>% 
  rename(Reference_Archetype = ReferenceArchetype_Archetype) %>% 
  mutate(across(where(is.character),as.factor)) %>% 
  mutate(AnchorUri = as.character(AnchorUri)) %>% 
  mutate(link = paste0(
    '<a href=\"',AnchorUri,'">',"link",'</a>'
    ),.before = 1  
    ) %>% 
  select(-AnchorUri) %>% 
  arrange(desc(Voting_result))


```

```{r model_prediction_print}
htmltools::tagList(
      DT::datatable(
        model_pred,
        colnames = str_replace_all(colnames(model_pred), "_", " "),
             callback = DT::JS(
      return_filter_js()
    ),
  filter = "top",
  rownames = FALSE,
  options = list(
  dom = "ltipr",
    searchCols = list(
    NULL,NULL,NULL,NULL,NULL,NULL,
    list(search = '... 0.3')
  ),
  autoWidth = TRUE,
  pageLength = 25),
  escape=FALSE
  )  %>%
  DT::formatPercentage(c("Voting_result","regression_proba","rando_forest_proba","knn_proba","decision_tree_c5_proba","xgboost_proba"),digits = 1)
  )
```
