---
title: "Matchup matrix"
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE} 
library(tidyverse)
library(plotly)
library(rwantshue)
# library(ggfittext)
# css: TOC.css
source("../sources/MTG_function_base_FB/global_mtg_sources.R")
source("../sources/S2_Source_mtg_new_card.R", local = TRUE)
source("../sources/sources_script_specific/S4_matrix_WR.R", local = TRUE)
params <- read_rds("../data/intermediate_result/temp_format_encours_for_param.rds")
conflicted::conflicts_prefer(dplyr::filter)
conflicted::conflicts_prefer(plotly::layout)
loaded_base_data <- readRDS(paste0("../data/", params$format_param, "_data_meta_en_cours.rds"))
# Je ne compte pas faire de matrix pour les SUB archetype pour le moment Car les sample sizes sont trop souvent ridicules a réfléchir
# Reflechir a inclusion player
#
# A reflechir :
# * WR including player perf
# * Combination

# X et Y en bilattérale
ratio_plot <- 3
# Generate different color scheme for close archetype
scheme <- iwanthue(seed = 42, force_init = TRUE) # recreate with a seed
```


```{r}
knitr::read_chunk("../sources/S1_introduction_text.R")
# Prendre en compte mieux le nombres de deck avec CI pour le best deck
```


```{r base_data_formating}
# Generate different color scheme for close archetype
df_base <- loaded_base_data %>%
  filter(Tournament != paste0(params$format_param, " League")) %>%
  group_by(Archetype) %>%
  mutate(
    Archetype_count = n()
  ) %>%
  ungroup() %>%
  group_by(Base_Archetype) %>%
  mutate(
    Base_Archetype_count = n()
  ) %>%
  ungroup() %>%
  arrange(Archetype_count)


Other_Archetype <- df_base %>%
  filter(Archetype_count < Archetype_cut_of_4 | Archetype == "Unknown") %>%
  pull(Archetype) %>%
  unique()

Other_base_Archetype <- df_base %>%
  filter(Base_Archetype_count < (Archetype_cut_of_4/2.5) | Base_Archetype == "Unknown") %>%
  pull(Base_Archetype) %>%
  unique()




df_base_all_data <- df_base %>%
  mutate(
    Archetype = ifelse(Archetype %in% Other_Archetype,
      "Other",
      Archetype
    ),
    Base_Archetype = ifelse(Base_Archetype %in% Other_base_Archetype,
      "Other",
      Base_Archetype
    ),
  ) %>%
  mutate(
    Archetype =
      factor(Archetype,
        level = unique(.$Archetype)
      ),
    Rank = as.numeric(
      factor(Archetype,
        level = rev(unique(.$Archetype))
      )
    ),
    Base_Archetype =
      factor(Base_Archetype,
        level = unique(.$Base_Archetype)
      )
  )


```


```{r winrate_matrix_computation}
Df_win_rate_matrix_simple_unnest_matchup <- df_base_all_data %>%
  rowwise() %>%
  filter(!is.null(Matchups)) %>%
  unnest_longer(Matchups) %>%
  unnest_wider(Matchups, names_sep = "_")

tournament_with_matchup <- unique(Df_win_rate_matrix_simple_unnest_matchup$TournamentFile)


Df_win_rate_matrix_correct_maccro_archetype_oppo <- Df_win_rate_matrix_simple_unnest_matchup %>%
  select(TournamentFile, Matchups_Opponent, Matchups_OpponentArchetype) %>%
  distinct(TournamentFile, Matchups_Opponent, Matchups_OpponentArchetype) %>%
  rename(Matchups_Opponent_basedArchetype = Matchups_OpponentArchetype) %>%
  group_by(TournamentFile, Matchups_Opponent) %>%
  left_join(
    Df_win_rate_matrix_simple_unnest_matchup %>%
      select(TournamentFile, Player, Archetype, Base_Archetype),
    by = c(
      "TournamentFile" = "TournamentFile",
      "Matchups_Opponent" = "Player"
    )
  ) %>%
  rename(
    Matchups_OpponentArchetype = Archetype,
    Matchups_OpponentBase_Archetype = Base_Archetype
  ) %>%
  mutate(
    Matchups_OpponentArchetype = as.character(Matchups_OpponentArchetype),
    Matchups_OpponentBase_Archetype = as.character(Matchups_OpponentBase_Archetype)
  ) %>%
  distinct()


Df_win_rate_matrix_base <- Df_win_rate_matrix_simple_unnest_matchup %>%
  select(-Matchups_OpponentArchetype) %>%
  inner_join(
    Df_win_rate_matrix_correct_maccro_archetype_oppo,
    by = c(
      "TournamentFile",
      "Matchups_Opponent"
    )
  ) %>%
  select(
    id, Meta, Week, Date, Archetype, Base_Archetype, Player,
    Matchups_Opponent, Matchups_OpponentArchetype, Matchups_OpponentBase_Archetype, Matchups_Wins,
    Matchups_Losses, Matchups_Draws, matches
  ) %>%
  mutate(
    # Matchups_Opponent_basedArchetype = Matchups_OpponentArchetype,
    Matchups_OpponentArchetype = ifelse(Matchups_OpponentArchetype %in% Other_Archetype,
      "Other",
      Matchups_OpponentArchetype
    ),
    Matchups_OpponentBase_Archetype = ifelse(Matchups_OpponentBase_Archetype %in% Other_base_Archetype,
      "Other",
      Matchups_OpponentBase_Archetype
    ),
    Matchups_OpponentArchetype = factor(Matchups_OpponentArchetype, levels = rev(levels(Archetype))),
    Matchups_OpponentBase_Archetype = factor(Matchups_OpponentBase_Archetype, levels = rev(levels(Base_Archetype)))
  )
```




```{r winrate_matrix_arch}
Df_win_rate_matrix_summarise <- win_rate_matrix_maker(
  df_fun = Df_win_rate_matrix_base,
  Archetype_type = "Archetype" # "Archetype" , "Base_Archetype"
)


Df_win_rate_matrix_format <- Df_win_rate_matrix_summarise %>%
  mutate(
    number_format_games = paste0("n = ", number_of_games, " [", Matchups_Wins, "-", Matchups_Losses, "]"),
    number_format_matches = paste0("n = ", number_of_matches, " [", Win_matches, "-", (number_of_matches - Win_matches), "]"),
    CI_WR_format_matches = paste0(round(WR_matches * 100, 1), "%", formating_CI(WR_matches, CI_WR_matches, round_val = 1, limit = c(0, 1))),
    CI_WR_format_games = paste0(round(WR_games * 100, 1), "%", formating_CI(WR_games, CI_WR_games, round_val = 1, limit = c(0, 1)))
  ) %>%
  mutate(
    CI_WR_sign_diff_0_games = CI_WR_sign_games != "0",
    CI_WR_sign_diff_0_matches = CI_WR_sign_matches != "0"
  )
```


```{r winrate_matrix_base_arch}
Df_win_rate_matrix_base_arch_summarise <- win_rate_matrix_maker(
  df_fun = Df_win_rate_matrix_base,
  Archetype_type = "Base_Archetype" # "Archetype" , "Base_Archetype"
)


Df_win_rate_matrix_base_arch_format <- Df_win_rate_matrix_base_arch_summarise %>%
  mutate(
    number_format_games = paste0("n = ", number_of_games, " [", Matchups_Wins, "-", Matchups_Losses, "]"),
    number_format_matches = paste0("n = ", number_of_matches, " [", Win_matches, "-", (number_of_matches - Win_matches), "]"),
    CI_WR_format_matches = paste0(round(WR_matches * 100, 1), "%", formating_CI(WR_matches, CI_WR_matches, round_val = 1, limit = c(0, 1))),
    CI_WR_format_games = paste0(round(WR_games * 100, 1), "%", formating_CI(WR_games, CI_WR_games, round_val = 1, limit = c(0, 1)))
  ) %>%
  mutate(
    CI_WR_sign_diff_0_games = CI_WR_sign_games != "0",
    CI_WR_sign_diff_0_matches = CI_WR_sign_matches != "0"
  ) %>%
  rename(
    Archetype = Base_Archetype,
    Matchups_OpponentArchetype = Matchups_OpponentBase_Archetype
  )
# %>%
#   filter(number_of_matches > 5)
# a <- table(Df_win_rate_matrix_base$Archetype,Df_win_rate_matrix_base$Base_Archetype) %>%
#   as.data.frame() %>%
#   filter(Freq > 0)


```


* All data : `r format(as.Date(min(Df_win_rate_matrix_simple_unnest_matchup$Date)), "%d-%m-%Y")` to `r format(as.Date(max(Df_win_rate_matrix_simple_unnest_matchup$Date)), format = "%d/%m/%Y")`. 
* Duration `r round(max(difftime(Sys.Date(),Df_win_rate_matrix_simple_unnest_matchup$Date,units = "weeks")),0)` weeks.
* Include meta : `r unique(Df_win_rate_matrix_simple_unnest_matchup$Meta)`.  
* Number of tournament : `r n_distinct(Df_win_rate_matrix_simple_unnest_matchup$TournamentFile)`
* With a total of `r nrow(Df_win_rate_matrix_base)` rounds of magic
* `r nrow(Df_win_rate_matrix_base %>% distinct(Archetype,Matchups_OpponentArchetype))` different matchup for archetypes.  
* `r nrow(Df_win_rate_matrix_base %>%   distinct(Base_Archetype,Matchups_OpponentBase_Archetype))` different matchup for base archetypes.  



```{r, Introduction_chunk_4_Deck_analysis, results='asis'}
```



Plot below show presence of each archetype in the matrix

```{r presence_plot}
#| column: screen
plot_presence_modify_for_matchup_matrix_fun(
     df_base = Df_win_rate_matrix_base,
    color_scheme =  scheme$hex(
  length(levels(Df_win_rate_matrix_base$Base_Archetype))
),
    plot_scaling = 2.25
)
```


# Archetype

For example, a score of 2-1 counts as 1 game won.

## Matrix
::: {.panel-tabset .nav-pills}
### Total matrix  

```{r res_arch_matrix}
plot_win_rate_mat(Df_win_rate_matrix_format, "matches")
```

### Only significative CI

```{r only_signif_mat_arch}
plot_win_rate_mat(Df_win_rate_matrix_format, "matches",
  # simplify_tab_ratio = 0.5,
  only_signif = TRUE
) %>% bslib::card(full_screen = TRUE)
```
:::

## CI plot 
```{r res_ci_plot_arch}
# <!-- #| column: screen -->
Archetype_ci_df_plot <- CI_plot_prepare_df_fun(Df_win_rate_matrix_format) %>%
  mutate(
    Archetype = factor(
      Archetype,
      levels = .$Archetype[order(.$Arch_winrate_matches + .$CI_Arch_winrate_matches)])
  ) %>% 
  arrange(Archetype)

Archetype_ci_df_plot_lines_df <- data.frame(
    yintercept = c(
        mean(Archetype_ci_df_plot$Arch_winrate_matches),
        mean(Archetype_ci_df_plot$Arch_winrate_matches - Archetype_ci_df_plot$CI_Arch_winrate_matches),
        mean(Archetype_ci_df_plot$Arch_winrate_matches + Archetype_ci_df_plot$CI_Arch_winrate_matches)
    ),
    line_type = c("Average Winrate",  "Lower CI", "Upper CI")
)


gg_ciplot_arch <- ggplot(data = Archetype_ci_df_plot,
                         aes(
                           text = paste(
        "Archetype: ", Archetype, "<br>", # Archetype name
        "Winrate: ",
        round(Arch_winrate_matches * 100, 1), " %",
        "[", round((Arch_winrate_matches + CI_Arch_winrate_matches) * 100, 2), ";",
        round((Arch_winrate_matches - CI_Arch_winrate_matches) * 100, 2), "]", "<br>",
        sep = ""
      )
      ) 
      ) +
  geom_point(
    aes(
      y = Arch_winrate_matches,
      x = Archetype
    ),
    position = position_dodge(0.75)
  ) +
  geom_errorbar(
    aes(
      x = Archetype,
      ymin = Arch_winrate_matches + CI_Arch_winrate_matches,
      ymax = Arch_winrate_matches - CI_Arch_winrate_matches
    ),
    position = position_dodge(width = .75), width = .01
  ) +
    geom_hline(
        data = Archetype_ci_df_plot_lines_df,
        aes(yintercept = yintercept, color = line_type),
        linetype = "dashed"
    ) +
    scale_color_manual(
        name = "Legend",
        values = c("Average Winrate" = "red", 
                   "Lower CI" = "blue", 
                   "Upper CI" = "blue")
    )  +
      scale_x_discrete(
        label = paste0(
    "<span style='font-size:", 17 , "px;'> <b>",
    Archetype_ci_df_plot %>%
      pull(Archetype) %>%
      unique(),
    "</b> </span>",
    "<br /> n : ", Archetype_ci_df_plot %>%
      pull(
        number_of_matches  
      ),
    "<br /> ", Archetype_ci_df_plot %>%
      mutate(temp_ci = paste0(
        round(Arch_winrate_matches * 100, 1), " %",
        "[", round((Arch_winrate_matches + CI_Arch_winrate_matches) * 100, 2), ";",
        round((Arch_winrate_matches - CI_Arch_winrate_matches) * 100, 2), "]")
        ) %>% 
      pull(
        temp_ci
      )

  ),
      )    +
  ylab("Winrate") +
  coord_flip()



gg_ciplot_arch %>%
  ggplotly(
    tooltip = c("text"),
      height = 50 * nrow(Archetype_ci_df_plot) #(480 * (ratio_plot+1)), width = (820 * (ratio_plot+1))
  )  %>%
    layout(
        legend = list(x = 0.85, y = 0.15) # Position précise de la légende dans le graphique Plotly
    ) %>%
    bslib::card(full_screen = TRUE)
```



# Base archetype

For example, a score of 2-1 counts as 1 game won.

## Matrix
::: {.panel-tabset .nav-pills}
### Total matrix  

```{r res_base_arch_matrix}
plot_win_rate_mat(Df_win_rate_matrix_base_arch_format, "matches")
```

### Only significative CI

```{r base_arch_only_signif_mat_arch}
plot_win_rate_mat(Df_win_rate_matrix_base_arch_format, "matches",
  # simplify_tab_ratio = 0.5,
  only_signif = TRUE
) %>% bslib::card(full_screen = TRUE)
```

:::


## CI plot 
```{r res_ci_plot_base_arch}
# <!-- #| column: screen -->
base_Archetype_ci_df_plot <- CI_plot_prepare_df_fun(Df_win_rate_matrix_base_arch_format) %>%
    mutate(
        Archetype = factor(
            Archetype,
            levels = .$Archetype[order(.$Arch_winrate_matches + .$CI_Arch_winrate_matches)]),
    ) %>% 
    arrange(Archetype)


base_Archetype_ci_df_plot_lines_df <- data.frame(
  yintercept = c(
    mean(base_Archetype_ci_df_plot$Arch_winrate_matches),
    mean(base_Archetype_ci_df_plot$Arch_winrate_matches - base_Archetype_ci_df_plot$CI_Arch_winrate_matches),
    mean(base_Archetype_ci_df_plot$Arch_winrate_matches + base_Archetype_ci_df_plot$CI_Arch_winrate_matches)
  ),
  line_type = c("Average Winrate", "Lower CI", "Upper CI")
)


gg_ciplot_base_arch <- ggplot(data = base_Archetype_ci_df_plot,aes(  text = paste(
        "Archetype: ", Archetype, "<br>", # Archetype name
        "Winrate: ",
        round(Arch_winrate_matches * 100, 1), " %",
        "[", round((Arch_winrate_matches + CI_Arch_winrate_matches) * 100, 2), ";",
        round((Arch_winrate_matches - CI_Arch_winrate_matches) * 100, 2), "]", "<br>",
        sep = ""
      ))
  ) +
  geom_point(
    aes(
      y = Arch_winrate_matches,
      x = Archetype,
    ),
    position = position_dodge(0.75)
  ) +
  geom_errorbar(
    aes(
      x = Archetype,
      ymin = Arch_winrate_matches + CI_Arch_winrate_matches,
      ymax = Arch_winrate_matches - CI_Arch_winrate_matches
    ),
    position = position_dodge(width = .75), width = .01
  ) +
  geom_hline(
    data = base_Archetype_ci_df_plot_lines_df,
    aes(yintercept = yintercept, color = line_type),
    linetype = "dashed"
  ) +
  scale_color_manual(
    name = "Legend",
    values = c("Average Winrate" = "red", 
               "Lower CI" = "blue", 
               "Upper CI" = "blue")
  )  +
  ylab("Winrate") +
    scale_x_discrete(
        label = paste0(
            "<span style='font-size:", 17 , "px;'> <b>",
            base_Archetype_ci_df_plot %>%
                pull(Archetype) %>%
                unique(),
            "</b> </span>",
            "<br /> n : ", base_Archetype_ci_df_plot %>%
                pull(
                    number_of_matches  
                ),
            "<br /> ", base_Archetype_ci_df_plot %>%
                mutate(temp_ci = paste0(
                    round(Arch_winrate_matches * 100, 1), " %",
                    "[", round((Arch_winrate_matches + CI_Arch_winrate_matches) * 100, 2), ";",
                    round((Arch_winrate_matches - CI_Arch_winrate_matches) * 100, 2), "]")
                ) %>% 
                pull(
                    temp_ci
                )
            
        ),
        # guide = guide_axis(n.dodge=3)
    ) +
  coord_flip() +
  theme(
    legend.position = c(0.85, 0.15),
    legend.background = element_rect(fill = "white", color = "black")
  )



gg_ciplot_base_arch %>%
  ggplotly(
    tooltip = c("text"),
    height = 50 * nrow(base_Archetype_ci_df_plot) #(480 * (ratio_plot+1)), width = (820 * (ratio_plot+1))
  )  %>%
  layout(
    legend = list(x = 0.85, y = 0.15) # Position précise de la légende dans le graphique Plotly
  ) %>%
  bslib::card(full_screen = TRUE)
```


#  Best deck 


Attempt to multiply the win rate matrix (WR or CI lower bound) by the weekly presence of the decks in order to calculate it, then divide by the total number of decks in order to calculate an average expected winrate for a given field.

Only decks with a CI are considered.

## Archetype 
```{r best_deck_computation}
Df_Expected_number_of_win_by_week <- df_base_all_data %>%
  group_by(Archetype, Week) %>%
  summarise(n = n(), .groups = "drop") %>%
  rename(Matchups_OpponentArchetype = Archetype) %>%
  full_join(
    Df_win_rate_matrix_summarise %>%
      filter(
        CI_WR_matches != 0,
        !is.na(CI_WR_matches)
      ) %>%
      mutate(lower_ci_bound = WR_matches + CI_WR_matches) %>%
      select(
        Archetype, WR_matches,
        lower_ci_bound,
        Matchups_OpponentArchetype
      ),
    by = c("Matchups_OpponentArchetype")
  ) %>%
  mutate(
    lower_ci_bound = replace(
      replace(lower_ci_bound, lower_ci_bound < 0, 0),
      lower_ci_bound > 1, 1
    ),
    lower_ci_bound = ifelse(Matchups_OpponentArchetype == Archetype,
      0.5, lower_ci_bound
    ),
    expected_win_WR = WR_matches * n,
    expected_win_lower_ci = lower_ci_bound * n
  ) %>%
  drop_na() %>%
  ungroup()



Df_expected_of_week_sum <- rbind(
  Df_Expected_number_of_win_by_week %>%
    mutate(Week = as.character(Week)) %>%
    group_by(Archetype, Week) %>%
    summarise(
      S_wr = sum(expected_win_WR), # /sum(n),
      S_ci = sum(expected_win_lower_ci), # / sum(n),
      .groups = "drop"
    ) %>%
    distinct(),
  Df_Expected_number_of_win_by_week %>%
    group_by(Archetype) %>%
    summarise(
      S_wr = sum(expected_win_WR), # / sum(n),
      S_ci = sum(expected_win_lower_ci), # / sum(n),
      Week = "All",
      .groups = "drop"
    ) %>%
    distinct()
) %>%
  mutate(
    Week = factor(
      Week,
      levels = c(1:max(df_base_all_data$Week), "All")
    )
  ) %>% 
  arrange(Week)


Df_wide_expected_of_week_sum <- Df_expected_of_week_sum %>%
  arrange(Week) %>%
  pivot_wider(
    names_from = Week,
    values_from = c(S_wr, S_ci)
  )
```



```{r spagheti_plot_arch_compute}
Presence_for_best_deck_plot <- rbind(
  Df_Expected_number_of_win_by_week %>%
    distinct(Matchups_OpponentArchetype, Week, n),
  Df_Expected_number_of_win_by_week %>%
    distinct(Matchups_OpponentArchetype, Week, n) %>%
    group_by(Matchups_OpponentArchetype) %>% summarise(
      n = sum(n),
      Week = "All",
      .groups = "drop"
    )
) %>%
  mutate(
    Week = factor(
      Week,
      levels = c(1:max(Df_Expected_number_of_win_by_week$Week), "All")
    )
  ) %>%
  group_by(Week) %>%
  mutate(
    Week_deck_number = sum(n),
    presence_percent = n / sum(n)
  )

# Génération du schéma de couleurs réduit de moitié
num_archetypes <- length(levels(Presence_for_best_deck_plot$Matchups_OpponentArchetype))
scheme <- iwanthue(seed = 42, force_init = TRUE)
colors_scales_presence <- scheme$hex(ceiling(num_archetypes / 2))  # Diviser le nombre de couleurs par 2

# Associer chaque Archetype avec une couleur et un style de ligne
archetype_levels <- levels(Presence_for_best_deck_plot$Matchups_OpponentArchetype)
archetype_styles <- rep(c("solid", "dashed"), length.out = num_archetypes)
colors_for_archetypes <- rep(colors_scales_presence, each = 2, length.out = num_archetypes)


plot_archetype_spaghetti <- (
  ggplot(
    Presence_for_best_deck_plot %>% 
      mutate(
        week = Week,
        Week_label = 
        paste0(
      "Week : ", Week, "<br>",
        "N total deck :<br>",Week_deck_number
                    )
    
      ),
    aes(
      x = Week,
      y = presence_percent,
      color = Matchups_OpponentArchetype,
linetype = Matchups_OpponentArchetype,
      text = paste(
        "Archetype: ", Matchups_OpponentArchetype, "<br>", # Archetype name
        "n : ", n, " (", round(presence_percent * 100, 2), " %)", "<br>",
        sep = ""
      ),
      group = 1
    )
  ) +
    geom_line(size = 1) +
    geom_point(size = 2) +
  scale_x_discrete(
    "Week",
    # breaks = levels(Presence_for_best_deck_plot$Week),
    labels = paste0(
      "Week : ", levels(Presence_for_best_deck_plot$Week), "<br>",
        # unique(Presence_Base_Archetype_for_best_deck_plot$Date), "<br>",
        "N total deck :<br>", Presence_for_best_deck_plot %>%
        arrange(Week) %>%  
        select(Week,Week_deck_number) %>% 
        distinct(Week,.keep_all = TRUE) %>% 
  pull(Week_deck_number)
                    )
  ) +
    scale_color_manual(
        values = setNames(colors_for_archetypes, archetype_levels)
    ) +
    scale_linetype_manual(
        values = setNames(archetype_styles, archetype_levels)  # Appliquer le style de ligne
    ) +
    ylab("Archetype presence") +
    scale_y_continuous(labels = function(x) scales::percent(x)) +
    theme(
      axis.title = element_blank(),
      panel.border = element_blank(),
      axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)
    )
) %>%
  ggplotly(tooltip = c("text"), height = (450 * 2.5), width = (850 * 2.5)) %>%
  plotly::layout(legend = list(
    orientation = "h",
    y = 1.1,
    title = list(text = "")
  ))
```

```{r print_spagheti_plot_arch}
#| column: screen
plot_archetype_spaghetti %>% bslib::card(full_screen = TRUE)
```


::: {.panel-tabset .nav-pills}
### Confidence intervalle lower bound
```{r best_deck_using_ci_res}
DT::datatable(
  Df_wide_expected_of_week_sum %>%
    select(Archetype, starts_with("S_ci_")) %>%
    rename_with(~ str_replace(., "S_ci_", "Week ")) %>% 
            arrange(desc(`Week All`)) %>% 
    select(Archetype,`Week All`,everything()),
  filter = "top", rownames = FALSE,
  callback = DT::JS(
    #         paste0(
    #         "var tips = ['",paste0(tooltips_deck_base,collapse = "','"),"'],
    #     header = table.columns().header();
    # for (var i = 0; i < tips.length; i++) {
    #   $(header[i]).attr('title', tips[i]);
    # }
    # ",
    return_filter_js()
    # )
  ),
  options = list(dom = "ltipr", autoWidth = TRUE, pageLength = nrow(Df_wide_expected_of_week_sum)),
  caption = htmltools::tags$caption(
    style = "caption-side: top; text-align: center; color:black;  font-size:200% ;",
    "Table : Best Archetype using Confidence intervalle lower bound"
  )
) %>%
  DT::formatRound(
    columns = 2:ncol(
      Df_wide_expected_of_week_sum %>%
        select(Archetype, starts_with("S_ci_"))
    ),
    digits = 0
  )
```




### Average Win rate

```{r best_using_average_res}
DT::datatable(
  Df_wide_expected_of_week_sum %>%
    select(Archetype, starts_with("S_wr_")) %>%
    rename_with(~ str_replace(., "S_wr_", "Week ")) %>% 
        arrange(desc(`Week All`)) %>% 
    select(Archetype,`Week All`,everything()),
  filter = "top", rownames = FALSE,
  callback = DT::JS(
    #         paste0(
    #         "var tips = ['",paste0(tooltips_deck_base,collapse = "','"),"'],
    #     header = table.columns().header();
    # for (var i = 0; i < tips.length; i++) {
    #   $(header[i]).attr('title', tips[i]);
    # }
    # ",
    return_filter_js()
    # )
  ),
  options = list(dom = "ltipr", autoWidth = TRUE, pageLength = nrow(Df_wide_expected_of_week_sum)),
  caption = htmltools::tags$caption(
    style = "caption-side: top; text-align: center; color:black;  font-size:200% ;",
    "Table : Archetype deck using Win rate"
  )
) %>%
  DT::formatRound(
    columns = 2:ncol(
      Df_wide_expected_of_week_sum %>%
        select(Archetype, starts_with("S_wr_"))
    ),
    digits = 0
  )
```

:::






## Base Archetype 
```{r best_deck_base_arch_computation}

Df_Base_Archetype_Expected_number_of_win_by_week <- df_base_all_data %>%
  group_by(Base_Archetype, Week) %>%
  summarise(n = n(), .groups = "drop") %>%
  rename(Matchups_OpponentBase_Archetype = Base_Archetype) %>%
  full_join(
    Df_win_rate_matrix_base_arch_summarise %>%
      filter(
        CI_WR_matches != 0,
        !is.na(CI_WR_matches)
      ) %>%
      mutate(lower_ci_bound = WR_matches + CI_WR_matches) %>%
      select(
        Base_Archetype, WR_matches,
        lower_ci_bound,
        Matchups_OpponentBase_Archetype
      ),
    by = c("Matchups_OpponentBase_Archetype")
  ) %>%
  mutate(
    lower_ci_bound = replace(
      replace(lower_ci_bound, lower_ci_bound < 0, 0),
      lower_ci_bound > 1, 1
    ),
    lower_ci_bound = ifelse(Matchups_OpponentBase_Archetype == Base_Archetype,
      0.5, lower_ci_bound
    ),
    expected_win_WR = WR_matches * n,
    expected_win_lower_ci = lower_ci_bound * n
  ) %>%
  drop_na() %>%
  ungroup()



Df_Base_Archetype_expected_of_week_sum <- rbind(
  Df_Base_Archetype_Expected_number_of_win_by_week %>%
    mutate(Week = as.character(Week)) %>%
    group_by(Base_Archetype, Week) %>%
    summarise(
      S_wr = sum(expected_win_WR), # /sum(n),
      S_ci = sum(expected_win_lower_ci), # / sum(n),
      .groups = "drop"
    ) %>%
    distinct(),
  Df_Base_Archetype_Expected_number_of_win_by_week %>%
    group_by(Base_Archetype) %>%
    summarise(
      S_wr = sum(expected_win_WR), # / sum(n),
      S_ci = sum(expected_win_lower_ci), # / sum(n),
      Week = "All",
      .groups = "drop"
    ) %>%
    distinct()
) %>%
  mutate(
    Week = factor(
      Week,
      levels = c(1:max(df_base_all_data$Week), "All")
    )
  )


Df_Base_Archetype_wide_expected_of_week_sum <- Df_Base_Archetype_expected_of_week_sum %>%
  arrange(Week) %>%
  pivot_wider(
    names_from = Week,
    values_from = c(S_wr, S_ci)
  )
```



```{r spagheti_plot_base_arch_compute}
Presence_Base_Archetype_for_best_deck_plot <- rbind(
  Df_Base_Archetype_Expected_number_of_win_by_week %>%
    distinct(Matchups_OpponentBase_Archetype, Week, n),
  Df_Base_Archetype_Expected_number_of_win_by_week %>%
    distinct(Matchups_OpponentBase_Archetype, Week, n) %>%
    group_by(Matchups_OpponentBase_Archetype) %>% summarise(
      n = sum(n),
      Week = "All",
      .groups = "drop"
    )
) %>%
  mutate(
    Week = factor(
      Week,
      levels = c(1:max(Df_Base_Archetype_Expected_number_of_win_by_week$Week), "All")
    )
  ) %>%
  group_by(Week) %>%
  mutate(
    Week_deck_number = sum(n),
    presence_percent = n / sum(n)
  )

# Génération du schéma de couleurs réduit de moitié
num_base_archetypes <- length(levels(Presence_Base_Archetype_for_best_deck_plot$Matchups_OpponentBase_Archetype))
scheme <- iwanthue(seed = 42, force_init = TRUE)
colors_scales_base_arch_presence <- scheme$hex(ceiling(num_base_archetypes / 2))  # Diviser le nombre de couleurs par 2

# Associer chaque Archetype avec une couleur et un style de ligne
base_archetype_levels <- levels(Presence_Base_Archetype_for_best_deck_plot$Matchups_OpponentBase_Archetype)
base_archetype_styles <- rep(c("solid", "dashed"), length.out = num_base_archetypes)
colors_for_base_archetypes <- rep(colors_scales_base_arch_presence, each = 2, length.out = num_base_archetypes)




plot_Base_Archetype_spaghetti <- (
  ggplot(
    Presence_Base_Archetype_for_best_deck_plot,
    aes(
      x = Week,
      y = presence_percent,
          color = Matchups_OpponentBase_Archetype,
      linetype = Matchups_OpponentBase_Archetype,  # Ajout du style de ligne
      text = paste(
        "Archetype: ", Matchups_OpponentBase_Archetype, "<br>", # Archetype name
        "n : ", n, " (", round(presence_percent * 100, 2), " %)", "<br>",
        sep = ""
      ),
      group = 1
    )
  ) +
    geom_line(size = 1) +  # Ajuster la taille des lignes pour une meilleure visibilité
    geom_point(size = 2) +  # Ajuster la taille des points
  scale_x_discrete(
    "Week",
    # breaks = levels(Presence_for_best_deck_plot$Week),
    labels = paste0(
      "Week : ", levels(Presence_Base_Archetype_for_best_deck_plot$Week), "<br>",
        # unique(Presence_Base_Archetype_for_best_deck_plot$Date), "<br>",
        "N total deck :<br>", Presence_Base_Archetype_for_best_deck_plot %>%
        arrange(Week) %>%  
        select(Week,Week_deck_number) %>% 
        distinct(Week,.keep_all = TRUE) %>% 
  pull(Week_deck_number)
                    )
  )  +
    scale_color_manual(
      values = setNames(colors_for_base_archetypes, base_archetype_levels)
    ) +
    scale_linetype_manual(
      values = setNames(base_archetype_styles, base_archetype_levels)  # Appliquer le style de ligne
    ) +
    ylab("Archetype presence") +
    scale_y_continuous(labels = function(x) scales::percent(x)) +
    theme(
      axis.title = element_blank(),
      panel.border = element_blank(),
         axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)
    )
) %>%
  ggplotly(tooltip = c("text"), height = (450 * 2.5), width = (850 * 2.5)) %>%
  plotly::layout(legend = list(
    orientation = "h",
    y = 1.1,
    title = list(text = "")
  ))
```

```{r spagheti_plot_base_arch_print}
#| column: screen
plot_Base_Archetype_spaghetti %>% bslib::card(full_screen = TRUE)
```


::: {.panel-tabset .nav-pills}
### Confidence intervalle lower bound
```{r best_deck_base_arch_using_ci_res}
DT::datatable(
  Df_Base_Archetype_wide_expected_of_week_sum %>%
    select(Base_Archetype, starts_with("S_ci_")) %>%
    rename_with(~ str_replace(., "S_ci_", "Week ")) %>% 
            arrange(desc(`Week All`)) %>% 
    select(Base_Archetype,`Week All`,everything()),
  filter = "top", rownames = FALSE,
  callback = DT::JS(
    #         paste0(
    #         "var tips = ['",paste0(tooltips_deck_base,collapse = "','"),"'],
    #     header = table.columns().header();
    # for (var i = 0; i < tips.length; i++) {
    #   $(header[i]).attr('title', tips[i]);
    # }
    # ",
    return_filter_js()
    # )
  ),
  options = list(dom = "ltipr", autoWidth = TRUE, pageLength = nrow(Df_Base_Archetype_wide_expected_of_week_sum)),
  caption = htmltools::tags$caption(
    style = "caption-side: top; text-align: center; color:black;  font-size:200% ;",
    "Table : Best base archetype using Confidence intervalle lower bound"
  )
) %>%
  DT::formatRound(
    columns = 2:ncol(
      Df_Base_Archetype_wide_expected_of_week_sum %>%
        select(Base_Archetype, starts_with("S_ci_"))
    ),
    digits = 0
  )
```


### Average Win rate

```{r best_deck_base_arch_using_average_res}
DT::datatable(
  Df_Base_Archetype_wide_expected_of_week_sum %>%
    select(Base_Archetype, starts_with("S_wr_")) %>%
    rename_with(~ str_replace(., "S_wr_", "Week ")) %>% 
        arrange(desc(`Week All`)) %>% 
    select(Base_Archetype,`Week All`,everything()),
  filter = "top", rownames = FALSE,
  callback = DT::JS(
    return_filter_js()
  ),
  options = list(dom = "ltipr", autoWidth = TRUE, pageLength = nrow(Df_Base_Archetype_wide_expected_of_week_sum)),
  caption = htmltools::tags$caption(
    style = "caption-side: top; text-align: center; color:black;  font-size:200% ;",
    "Table : Best Base Archetype using Win rate"
  )
) %>%
  DT::formatRound(
    columns = 2:ncol(
      Df_Base_Archetype_wide_expected_of_week_sum %>%
        select(Base_Archetype, starts_with("S_wr_"))
    ),
    digits = 0
  )
```

:::

