---
title: "Readme magic data analysis"
author: François Bettega
date: "`r Sys.Date()`"
output:
  md_document:
    variant: gfm
---


```{r setup, include=FALSE, message = FALSE, warning = FALSE} 
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
source("../sources/MTG_function_base_FB/global_mtg_sources.R")
```


# Modern_data_analysis
Personal verion of magic metagame analysis

Result are avaible [here](https://mtg-modern.serveur-du-placard.xyz/)  


## Dependencies
**Warning**: I've tried to make this script as reproducible as possible, but as it wasn't my initial intention, some of the details may be missing.  I may have forgotten some packages or folders that are necessary for the script to work properly.  


### Github repo and script
The initial json is obtained from the [badaro parser](https://github.com/Badaro/MTGOArchetypeParser).   


Normally the pull of the necessary github repo is automatic (to clone the repos concerned, simply uncomment the git clone lines in the  [S0_one_file_to_rule_them_all.R file](./S0_one_file_to_rule_them_all.R) ).

**Currently the automatic github pull does not work because to obtain results similar to mine it is necessary to merge in Archetype parser the decklist cach repo of [Badaro](https://github.com/Badaro/MTGODecklistCache) and [Jiliac](https://github.com/Jiliac/MTGODecklistCache/).**
Format data pull is automatic but can also be found [here](https://github.com/Badaro/MTGOFormatData) 

To get scryfall data in csv i use my own script you can find it [here](https://github.com/fbettega/fetch_scryfall_data_to_csv) file generated should be put in  'Modern_data_analysis\data\mtg_data'.   

### Packages

Install packages script can be found [here](../sources/S3_install_packages.R)  

List of package below :  


```{r}
list.of.packages <- readr::read_rds("../data/list_of_packages.rds")
list.of.packages %>%
  select(package) %>% 
  knitr::kable(format = "pipe")
```


## format includes
Table below list format includes and starting date
```{r format_table_print, results='asis'}
format_date_en_cours_fulltable <- read.csv("../other_file/format_handle.csv")
format_date_en_cours_fulltable %>% 
  rename(
    Format = format_param,
    `Start date` = date_cutoff) %>% 
  knitr::kable(format = "pipe")
```




## Base data format

|          Column name         	|    Type    	|                                                       Definition                                                       	|
|:----------------------------:	|:----------:	|:----------------------------------------------------------------------------------------------------------------------:	|
|              id              	|  Integer   	|                                          unique file id (for unnest of lists)                                          	|
|          Tournament          	| Character  	| the type of tournament (note that leauges can cause problems because only 5-0s are in the file, so survivor bias ++++) 	|
|             Meta             	| Character  	|                                 large time unit (large change extension output or ban)                                 	|
|             Week             	|  Integer   	|                                                   number of the week                                                   	|
|             Date             	|    Date    	|                                                     Tournament date                                                    	|
|            Result            	| Character  	|                                     tournament results, column varies by tournament                                    	|
|              Points          	| Character  	|                                       sum of results (win = 3 Losse = 0 Draw = 1)                                      	|
|              Win             	|  Integer   	|                                                     number of wins                                                     	|
|             Loss             	|  Integer   	|                                                     number of loss                                                     	|
|             Draw             	|  Integer   	|                                                     number of draw                                                     	|
|           Player             	| Character  	|                                                       Player name                                                      	|
|           AnchorUri          	| Character  	|                                                   Url of the decklist                                                  	|
|          Archetype           	| Character  	|        the archetype from the parser modified by FB and aggregated by the initial scrypt into a macro archetype.       	|
|             Color            	| Character  	|                             deck colour (U = Blue, G : Green, R : Red, B : black, W: White)                            	|
|           Companion          	| Character  	|                                          specific type of card defining decks                                          	|
| ReferenceArchetype_Archetype 	| Character  	|                                 archetype of deck obtained with badaro's initial parser                                	|
|   ReferenceArchetype_Color   	| Character  	|          deck colour obtained with badaro's initial parser (U = Blue, G : Green, R : Red, B : black, W: White)         	|
| ReferenceArchetype_Companion 	| Character  	|                       specific type of card defining decks obtained with badaro's initial parser                       	|
|           Mainboard          	|    List    	|                                                   Mainboard decklist                                                   	|
|           Sideboard          	|    List    	|                                                   Sideboard decklist                                                   	|
|           Matchups           	|    List    	|                                                    List of matchupes                                                   	|
|            Matches           	|  Integer   	|                                                number of matches played                                                	|
|        Base_Archetype        	| Character  	|        the archetype from the parser modified by FB and aggregated by the initial scrypt into a macro archetype.        |   
|        Archetype_count       	|  Integer   	|                                 Number of times the Archetype is present in the dataset                                	|



## Outpout

A quarto book for each format define above


## Warning
**Grid Search can be really long around 3 days for me**  
A downloadable version of the grid search results for each model is available [here](https://mtg-modern.serveur-du-placard.xyz/grid_dl/grid.zip) **Warning aroud 4 Go**.

